---
title: "Chord sequence"
author: "Mikkel Meyer Andersen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chord sequence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "#>"
)
```

```{r}
library(ggplot2)
library(forcats)
library(dplyr)
library(pichor)
```

# Minimal example

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = list(c(1, 2, 3), c(2, 3, 4))) %>% 
  ggpiano(labels = FALSE) + 
  facet_wrap(~ seq_no)
```

# Slightly larger example


"Let it be" by Beatles has initially chords G, D, Em, C, G, D, C.

```{r}
choords <- list(construct_chord_major("G"),
                construct_chord_major("D"),
                construct_chord_minor("E"), # Em
                construct_chord_major("C"),
                construct_chord_major("G"),
                construct_chord_major("D"),
                construct_chord_major("C"))
choords
choord_names <- sapply(choords, capture.output)
```

```{r}
key_seq <- lapply(choords, get_keys)
#key_seq <- lapply(choords, get_keys_inversion, inversion = 0L)
```

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = key_seq) %>% 
  ggpiano(labels = FALSE) + 
  facet_wrap(~ seq_no)
```

And get more helpful facet panel title:

```{r}
d_chord_nms <- tibble::enframe(choord_names, name = "seq_no", value = "seq_nm")
d <- keys_coords %>% 
  highlight_key_sequence(key_sequence = key_seq) %>% 
  left_join(d_chord_nms, by = "seq_no") %>% 
  mutate(seq_lbl = paste0(seq_no, "(", seq_nm, ")")) %>% 
  mutate(seq_lbl = forcats::fct_inorder(seq_lbl))
```

```{r}
d %>% 
  ggpiano(labels = FALSE) + 
  facet_wrap(~ seq_lbl)
```


# Finding better inversions

Currently only one method is available for finding better inversions. 
It is minimising the distances between keys in consecutive chords. 
And with an exhaustive approach that is only feasible for shorter sequences. 

```{r}
key_seq
opt_res <- optim_min_dist_exhaustive(key_sequence = key_seq)
opt_res
```

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = opt_res$best) %>% 
  left_join(d_chord_nms, by = "seq_no") %>% 
  mutate(seq_lbl = paste0(seq_no, "(", seq_nm, ")")) %>% 
  mutate(seq_lbl = forcats::fct_inorder(seq_lbl)) %>% 
  ggpiano(labels = FALSE) + 
  facet_wrap(~ seq_lbl) +
  labs(title = "Best inversions")
```

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = opt_res$worst) %>% 
  left_join(d_chord_nms, by = "seq_no") %>% 
  mutate(seq_lbl = paste0(seq_no, "(", seq_nm, ")")) %>% 
  mutate(seq_lbl = forcats::fct_inorder(seq_lbl)) %>% 
  ggpiano(labels = FALSE) + 
  facet_wrap(~ seq_lbl) +
  labs(title = "Worst inversions")
```


