---
title: "Chord sequence"
author: "Mikkel Meyer Andersen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chord sequence}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  fig.width = 8,
  fig.height = 4,
  comment = "#>"
)
```

```{r}
library(ggplot2)
library(forcats)
library(dplyr)
library(pichor)
```

# Minimal example

```{r, fig.height = 2}
keys_coords %>% 
  highlight_key_sequence(key_sequence = list(c(1, 2, 3), c(2, 3, 4))) %>% 
  ggpiano() + 
  facet_wrap(~ seq_name)
```

# Slightly larger example

A version of "Let it be" by Beatles initially has chords G, D, Em, C, G, D, C.

```{r}
chords <- list(construct_chord_major("G"),
               construct_chord_major("D"),
               construct_chord_minor("E"), # Em
               construct_chord_major("C"),
               construct_chord_major("G"),
               construct_chord_major("D"),
               construct_chord_major("C"))
chords
chord_names <- sapply(chords, as.character, brief = TRUE)
```

```{r}
key_seq <- lapply(chords, get_keys)
```

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = key_seq) %>% 
  ggpiano() + 
  facet_wrap(~ seq_name)
```

And get more helpful facet panel title by providing `sequence_names` argument to `highlight_key_sequence`:

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = key_seq,
                         sequence_names = chord_names) %>% 
  ggpiano() + 
  facet_wrap(~ seq_name)
```

And for exmple include `seq_no` in a new column `seq_lbl` (that are then converted to a factor with the right ordering):

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = key_seq,
                         sequence_names = chord_names) %>% 
  mutate(seq_lbl = paste0(seq_name, " (#", seq_no, ")")) %>% 
  mutate(seq_lbl = forcats::fct_inorder(seq_lbl)) %>% 
  ggpiano() + 
  facet_wrap(~ seq_lbl)
```


# Finding better inversions

Currently only one method is available for finding better inversions. 
It is minimising the distances between keys in consecutive chords, where 
distance is the number of keys not used anymore plus new keys.  
And with an exhaustive approach that is only feasible for shorter sequences. 

```{r}
opt_res <- optim_min_dist_exhaustive(key_sequence = key_seq)
```

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = opt_res$best,
                         sequence_names = chord_names) %>% 
  ggpiano() + 
  facet_wrap(~ seq_name) +
  labs(title = "Best inversions")
```

```{r}
keys_coords %>% 
  highlight_key_sequence(key_sequence = opt_res$best,
                         sequence_names = chord_names) %>% 
  ggpiano() + 
  facet_wrap(~ seq_name) +
  labs(title = "Worst inversions")
```



# Bigger example

```{r}
chords <- list(
  list(chord = construct_chord_major("G"), 
       highest_tone = "G"),
  
  list(chord = construct_chord_minor("B"), 
       highest_tone = "F#"),
  
  list(chord = construct_chord_major("C"), 
       highest_tone = "E"),
  
  list(chord = construct_chord_major("G"), 
       highest_tone = "D")
)
```

```{r}
chord_keys <- lapply(chords, function(x) get_keys_highest_tone(x$chord, x$highest_tone))
chord_names <- lapply(chords, function(x) paste0(
  as.character(x$chord, brief = TRUE), 
  " with ", x$highest_tone, " highest"))

keys_coords %>% 
  highlight_key_sequence(key_sequence = chord_keys,
                         sequence_names = chord_names) %>% 
  ggpiano() + 
  facet_wrap(~ seq_name)
```
